\chapter*{Abstract}

Writing \acrfullpl{sc} are hard. Writing secure \acrshortpl{sc} is even harder. Automatic code generation is by many considered the ”holy grail” in the field of computer science. Recent advances in transformer models have shown great potential in the area of synthesizing code from code comments. However, it is just as important \textit{how} these models are best put to use. In this thesis, it is investigated: how to automatically generate \acrlong{sc} code with transformer-based language models, by inputting comments to guide the code generation? Due to the monetary and immutable nature of blockchain, security in \acrshortpl{sc} is of uttermost importance. This thesis also investigates: how to generate secure \acrlong{sc} code with transformer-based language models? A design science research approach is adopted for answering these research questions. For automatically synthesizing \acrshort{sc} code, the 6 billion parameter model GPT-J by EleutherAI is fine-tuned on \acrshort{sc} code. For this task, the currently largest dataset of real \acrshort{sc} code is constructed, containing 186,397 contracts. To evaluate the comment-aid approach to generate code, the original code was used as the ground truth. This code was then compared with the generated code, and their differences were measured using the \acrfull{bleu} score. Results of the evaluation show that this approach results in a \acrshort{bleu} score of 0.557, which is beyond the state-of-the-art. For generating secure \acrlong{sc} code with transformer-based language models, a novel method named security conditioning is proposed. From both automatic and manual evaluation of the technique, the evaluation results show that security conditioning produced secure code.


%One sentence of
%- Your research motivation (argue why it is important to do your study)
%- List research questions 
%- Briefly explain the research methods
%- Summarize research results and main contributions (results and contributions should be linked to your research questions)
%
%To sell the idea and main results of your thesis




